term papaer 2

### 2024-02-13 outputs/paper/paper.qmd
paper

@@

```{r}
#| label: fig-model
#| fig-cap: "Tabulated weights of linear regression models 1 through 6 using ordinary least squares. In parentheses are the standard errors. Asterisks denote ranges of p-values as described in the table footer."
#| echo: false
#| message: false
#| warning: false

>>>>

```{r}
#| label: fig-model
#| fig-cap: "umemployment rate Vs low income rate"
#| echo: false
#| message: false
#| warning: false

@@
